\section*{Experience}
	\begin{workExperience}{Luminis, Arnhem}%
	{Software Developer}{\period{\moment{Augustus}{2011}}{\present}}	
                Daan contributes as a software developer for Luminis
                to the following projects.
                
                \activity{NPO}
                NPO is a dutch broad casting company. NPO wanted a
                better insight into viewer ratings. The current
                solution missed usage by tablet and smartphone users.
                by analysing the logs and creating viewer events the
                missing information was provided.
                Daan contributed to this project by creating a test
                framework that could easily setup log lines and verify
                the expected results so the project could be automatic
                tested. 
                \technics Node, Redis, JavaScript, Mocha, Jake, git

                \activity{van Dijk}
                Van Dijk is a publisher of school books. Daan
                Contributed to the project by creating load and
                performance test on the webshop and aiding in the
                development of new functionality and resolution of bugs.
                \technics Groovy, Grails, JavaScript, Bamboo,
                Confluence, Jira, JMeter, svn, git

                \activity{CHARTER}
                CHARTER is a european research agreement between
                universities and business partners. Daan developed for
                Thales a Radar Tracking simulation that was used to
                test the new development tools produced by CHARTER.
                \technics Java, Bamboo, Confluence, Jira, JML, svn

                \activity{RTL 365}
                RTL is a television broadcasting company. RTL news
                releas a news app for the IPad. Daan created a content
                managment system that allowed editors to determine
                what news would be placed in the app.
                \technics o.a Groovy, Grails, Bamboo, Confluence,
                Jira, MySQL, svn
	\end{workExperience}

	\begin{workExperience}{Topicus Zorg, Deventer}%
	{Informatie architect}{\period{\moment{Juni}{2009}}{\moment{Juli}{2011}}}
                As a software developer Daan contributed to the
                following projects

		\activity{Protopics HAP}
                Protopics HAP is a information managment application
                for the healthcare provisioners. It allows the
                registration of patients and aids docters in upholding
                the national standard practices.
                Daan shaped several key components of the system,
                notably Track \& Trace and working by Protocol.
		\technics o.a. Java, Eclipse, Maven, Wicket, Hibernate, Postgres,
		Spring, SQL, Oracle, Pgadmin, Liquibase, JAX-WS, JQuery, Javascript
		
		\activity{Protopics KIS}
                Daan contributed to Protocis KIS. Protopics KIS help
                monotoring patients with complicated health problems.
		\technics o.a Java, Eclipse, Wicket, Hibernate, Spring, SQL, Oracle,
		Pgadmin, Liquibase
		
		\activity{Internship Guide}
                Daan guided several interns through their internship.
		
		\activity{Community Outreach}
                Daan was responsible for various Community Outreach
                events. Notable examples are presenting for groups of
                students and organizing a workshop for students.
		
		\activity{Framework Development}
                For Topicus Daan developed various frameworks. For
                example, by using AspectJ Daan created an hibernate
                Model for a Wicket Application.
		\technics AspectJ, Wicket, Design Patterns
	\end{workExperience}

	\begin{workExperience}{Sogyo B.V., de Bilt}%
	{Software Developer}{\period{\moment{Juni}{2008}}{\moment{Juni}{2009}}}
                Daan contributed to various projects as a software
                developer, among them are
		
		\activity{Pilot Masterclass Agile Software Ontwikkeling}
                Daan participated in a pilot for agile software
                development. The pilot entailed setting up a continous
                build environment with issue tracking, source control
                repository and a community wiki. The use case was to develop a
                library application.
		\technics o.a. Java, TestNG, Seam, JSF, Ant, svn, TeamCity, Trac, Agilo.
		
		\activity{Sogyo Interactive Graphics}
                This project entails the creating of a project
                planning module. It should aid a project manager with
                a visual way of determining which team member is
                available for a project, and for how much time.
                It explored the new JavaFX technologie by creating a
                client interface upon a java backend.
		\technics o.a. Java, JavaFX, JUnit, XML, XSLT, XPath, Tomcat, HTML,
		JavaScript, CSS, JSP, Servlets, Maven, Perl, Latex, Trac, Agilo, Flex,
		C\#, svn, Hudson, SCRUM.

	\end{workExperience}
	
	\begin{workExperience}{SumOfUs, Nijmegen}%
	{Software Developer}%
	{\period{\moment[01]{07}{2006}}{\moment[01]{08}{2006}}}
                Daan created a PostScript script to print hundred of
                score cards for the Nijmegen Math Competion.
		\technics o.a. Perl, Postscript.
	\end{workExperience}

	\begin{workExperience}{Ratio, Nijmegen}%
	{Software Developer}%
	{\period{\moment[01]{01}{2001}}{\moment[01]{01}{2005}}}
                This project had as goal to create a mathematics
                curriculum for gifted highschool studends on the web.
		\technics o.a. Perl, HTML, CSS, JavaScript.	
	\end{workExperience}
